Commit Rater

### 2015-08-25 presentations/paper/research_question.tex

>>>>

The original inspiration for this work was the project \emph{Commit} \emph{Logs} \emph{From} \emph{Last} \emph{Night}\cite{LastNight}, especially its presentation resulting from it\footnote{\url{https://www.youtube.com/watch?v=V44kscaJe3M}}. Now defunct and only a static site, it used to regularly extract the latest commit messages from GitHub for vulgarity and published them on the website. As seen in the presentation, the vulgarity rate can be correlated with various software languages, time of day et cetera. However, in the end it is merely a fun website and does not give any useful information to developers.

Similarly, the paper \emph{Sentiment} \emph{Analysis} \emph{of} \emph{Commit} \emph{Comments} \emph{in} \emph{GitHub:} \emph{An} \emph{Empirical} \emph{Study}\cite{Sentiment} from the MSR conference 2014 analyzes commit messages from Git repositories for their emotional impact and their correlation to software languages, time of day, geographical distribution and project approval. Again, however, the result is merely reflective not useful for developers in the process of developing something, which was our primary goal in this research.
